Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-07-11 prop_letter.tex
prop_letter.tex Introduction Updating...

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality\nb\cite{BarrettKent2004,Appleby_2005}.  For example,
Meyer\nb\cite{PhysRevLett.83.3751} and Mermin\nb\cite{Mermin1999} disagree
on whether finite-precision measurements invalidate the Kochen-Specker
theorem\nb\cite{kochenspecker1967,peres1995quantum}, and discussion
has continued on whether contextuality is consistent with  experimental outcomes\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
fundamental question is how to make mathematical theories of quantum mechanics that are intrinsically, rather than only implicitly, consistent with the resources available for the realistic accuracy of an actual measurement.

>>>>

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality\nb\cite{BarrettKent2004,Appleby_2005}.  For example,
Meyer\nb\cite{PhysRevLett.83.3751} and Mermin\nb\cite{Mermin1999} disagree
on whether finite-precision measurements invalidate the Kochen-Specker
theorem\nb\cite{kochenspecker1967,peres1995quantum}. In particular,
the Kochen-Specker theorem is based on the two sphere\nb$S^{2}$
cannot be colored by red and green such that any orthogonal basis
has exactly one red vector. On the one hand, Meyer argued that the
rational dense subset of $S^{2}$, $S^{2}\cap\mathbb{Q}^{3}$, is
colorable, and we cannot distinguish $S^{2}$ and $S^{2}\cap\mathbb{Q}^{3}$
since finite precision measurement\nb\citep{PhysRevLett.83.3751,Szangolies2015}.
On the another hand, Mermin argued any physical outcome must be a
continuous function on the experimental configuration\nb\citep{Mermin1999,Szangolies2015}.
Discussion
has continued on whether contextuality is consistent with  experimental outcomes\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}. The
fundamental question is how to make mathematical theories of quantum mechanics that are intrinsically, rather than only implicitly, consistent with the resources available for the realistic accuracy of an actual measurement.
